



In this section, we discuss the architecture of EcoDrive and 
possible applications.


\subsection{EcoDrive Architecture}

EcoDrive reads real-time OBD parameters through OBD port
and controls air/fuel injection rate by emulating the gas pedal.
We illustrate the architecture of EcoDrive in Fig. \ref{ecodrive}.
The sensed parameters from OBD port are passed to modeling component
to train the models.
The modeling component builds an AFR profile to 
record the instant fuel consumptions of various 
accelerations at different speeds.
Based on pre-calculated driving strategy and real-time sensed vehicular speed, 
the controlling component controls air/fuel injection rate to adjust vehicular speed by 
sending the gas pedal position values to the ECU. 
To emulate the gas pedal, we utilize the drive-by-wire technology, 
where the gas pedal and throttle are connected by electronic messaging instead of mechanical linkage.   
It enables the position of gas pedal can be sent as a message
to control throttle position. 
The throttle controls the volume of air flow injected into the engine. 
 


\subsection{Applications}

EcoDrive is used as an independent system that can be installed
on regular vehicles.  
It can be used as a control system in a way similar to 
cruise control \cite{cruise_control, bengtsson2001adaptive, ioannou1993autonomous}. 
In this application, it is used as a EcoDrive mode that a human driver
can switch it on or off. 
Drivers are required to press the brake pedal to turn this mode off
to keep safe distance to front car or traffic lights/signs accordingly.
This mode can be integrated with intelligent front object or traffic light detection
systems \cite{bengtsson2001adaptive, ioannou1993autonomous} 
to further enhance driving experience. 
EcoDrive requires two inputs, the speed limit and road length. 
The speed limit can be specified by human driver or obtained from online database \cite{speedlimit}. 
The road length can be calculated by a navigation software.



It can also be used as a subsystem of autonomous driving systems 
\cite{googledriverlesscar, urmson2008autonomous, litman2013autonomous, kim2013towards}. 
We envision a highly autonomous and intelligent system that all the route
information are pre-calculated, e.g., speed limit, traffic conditions and
distances of each road segment etc. 
EcoDrive can be used as a subsystem to predict fuel consumption
of possible routes \cite{ganti2010greengps} and 
calculate the optimal driving strategy.  


