


\chapter{RTDrive: Augmenting Self-Driving with Remote Control}
\label{chapter_rtdrive}

Self-driving systems are being designed in recent years 
to improve road safety by replacing human drivers. 
In spite of many advances so far, it is unlikely that such systems are
going to achieve perfect accuracy under all conditions. In
particular, occasional failures are anticipated when such vehicles
encounter situations not observed before. Under such
infrequent failure scenarios, the research community has so
far, considered two alternatives — to return control to the
driver in the vehicle, which has its own challenges and limitations,
or to attempt to safely “park” the vehicle out of
harm’s way. We consider a viable third alternative — on
failure of the self-driving function in the vehicle, the system
could return control to a remote human driver. This remote
human driver will augment the self-driving system in vehicles,
only when failures occur, which may be due to bad
weather, malfunction, contradiction in sensory inputs, and
other such conditions.
In this chapter, we present a framework called
RTDrive, where the remote driver can view the vehicle’s sensory
data and control the vehicle in real time.
It includes several modules to improve video encoding
efficiency and remote control experience, which are
presented in the rest of this chapter. 


\section{Motivation}

\input{rtdrive/motivation.tex}


\section{The Design of RTDrive}

\input{rtdrive/design.tex}



\section{Implementation}

\input{rtdrive/implementation.tex}


\section{Experimental Results}

\input{rtdrive/evaluation.tex}


\section{Summary of RTDrive}

\input{rtdrive/conclusion.tex}





\input{rtdrive/appendix.tex}


